MCC Kids Model Predictions

### 2019-02-11 stats/kids/kids_model_predictions.Rmd
partially repair noise induced rsa bda model

   var ageConditionSpecificData =  _.filter(ex3Data, {age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})

@@

    map(function(d){ 
      observe(noisyRsaPredictions_diff_cong, d.correct_inf)
    }, ageConditionSpecificData)

@@

@@

```{r}
noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
  data =list(ex3data = ex3_data, modelParams = model_params_by_age, ageConditions = ageConditions),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
)

>>>>

   var ageConditionSpecificData =  _.filter(ex3Data, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
    var speakerOptimality = age_bin.so_map

@@

    var noisyRsaPredictions_diff_cong = addNoise(rsaPredictions_diff_cong, noise)

    map(function(d){ 
    observe(noisyRsaPredictions_diff_cong, d.correct_inf)
    }, ageConditionSpecificData)
  // display(conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment)
  // display(Math.exp(noisyRsaPredictions_diff_cong.score(1)))

@@

  }
  var predictions_by_age = map(predict_by_age, modelParams)
  display(JSON.stringify(predictions_by_age))
  return predictions_by_age
}

@@

```{r}
noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
  data =list(ex3data = ex3_data %>% mutate(binned_age = as.numeric(as.character(binned_age))), 
             modelParams = model_params_by_age, 
             ageConditions = ageConditions),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
)
